\cvsection{Experience}
\begin{cventries}
  \cventry
    {Creating \& Developing \& Learning}    
    {Freelance \& Personal Projects}
    {My house, San Francisco, CA}
    {Then - Always}
    {
      \begin{cvitems}
        \item {Building a static-ish site for a Computational Materials research group at the University of California Riverside utilizing AWS tools: hosted on S3 with API Microservices and lambda functions to handle dynamic content.} 
        \item {Technical goals for this freelance project include maximizing use of flexbox, using npm for all build steps, creating custom node scripts to compile pug templates and parse \href{http://www.bibtex.org/About}{bibtex} journal citations into json format.}      
        \item { Built \href{http://autumnfjeld.com}{autumnfjeld.com} with the help of a pre-designed the HTML/CSS template and made it my own, which has been a great learning experience in design and layout. Broke up the HTML into pug files, storing my content as json to compile into a static site stored on AWS S3.} 
        \item {Gave AWS Microservices a spin for the contact form in autumnfjeld.com. Connected my email to this domain via Simple Email Service and wired up a Lambda function to email the form content from my API endpoint to myself.} 
        \item {Improving my design skills. Currently enrolled in Coursera's Graphic Design Specialization created by California Institute of the Arts.} 
      \end{cvitems}
    }
    
  \cventry
    {Passive recruiting software}
    {Software Engineer - TalentBin by Monster}    
    {San Francisco, CA}
    {April 2016 - present}
    {
      \begin{cvitems}
        \item {Full-stack software engineer, with front-end emphasis. Build and maintain enterprise recruiting web application. Tech stack: Java, PHP, Javascript (Backbone, Ractive).}
        \item {Enforce good design and provide constructive criticism on our UI as much as possible. Am engaged with product manager and design team in a major redesign of our enterprise site--learning about a large scale redesign process and offering a front-end engineer perspective.}
        \item {Propose new code patterns with modern frameworks to replace, or coexist with legacy code.}
        \item {Building a chrome extension app: a mini-version of our main site that pulls data from social network sites to match profiles in our db.}
        \item {Help a growing team migrate from start-up culture to a well-defined agile-scrum work process. Creating documentation, proactively recommend improvements in communication and tools (git, slack, zapier, etc.).}
        \item {Motivate our dev team to share technical learnings and challenges in regular lunch \& learn sessions.}
        \item {Each summer have supervised two computer science interns, guiding them through the complexities of a large codebase and teaching them in first experiences in front-end web development.}
      \end{cvitems}
    }
    
  \cventry
    {Mobile shopping organizer and retail portal for retailer to consumer rewards}
    {Senior Front End Developer{\enskip\cdotp\enskip}Ziploop }
    {Orinda, CA}
    {April 2014 - April 2016}
    {
      \begin{cvitems}
        \item {Designed and implemented front-end components of mobile consumer app and two enterprise sites in AngularJS framework. Worked closely with President to design UI/UX.}
        \item {Collaborated with founding CTO to architect components, maintain build processes (grunt, gulp, git, unix scripts), choose frameworks, modules, and pushed to keep a clean, maintainable code base.}
        \item {Refactored many parts of chaotic, legacy codebase to maintainability and sanity (SASS, Angular best practices)
        \item Solved load time problems for large list of images, optimizing quality and performance; continually strove for pixel perfect UI/UX.}
        \item {Managed collaborations between lead developer and non-technical president, supervised two junior engineers and an assistant to develop her technical graphic design skills.}
      \end{cvitems}
    }
 
  \cventry
    {Project based software immersive course}
    {Student{\enskip\cdotp\enskip} Hack Reactor}
    {San Francisco}
    {January 2014 - April 2014}
    {
      \begin{cvitems}
        \item {Part of a team contracted to develop a prototype fora  commercial app. Designed back-end schema in Firebase, chosen for Simplelogin authentication, direct database reference binding.}
        \item {Built app in AngularJS architecture, ported to mobile with Cordova and styled with Ionic. Careful attention given to AngularJS controller and service modularity to create efficient team work-flow.}
        \item {Built a d3.js interactive force directed graph as an AngularJS directive, allowing users to click on a url-node to create an expansive node map of Wikipedia articles. {\tiny \url{http://wikiviz.herokuapp.com}}}
      \end{cvitems} 
    }
    
  \cventry
    {Engineering Support/Consulting \& Business Development}
    {Technical Support Engineer – NUMECA International}
    {San Francisco, CA}
    {November 2010 - July 2013}
    {
      \begin{cvitems}
        \item {Provided consulting support to engineers at Boeing, Honeywell, etc. on using NUMECA’s computational fluid dynamics software tools, delivering solutions in meshing, solver setup, and post-processing.}
        \item {Improved fluid dynamics and meshing software as an integral part of the feedback loop for identifying and troubleshooting software bugs, user-friendliness, and scientific accuracy issues.}
        \item Created and delivered technical training webinars twice a month to NUMECA’s user base.
      \end{cvitems}
    }
    
  \cventry
    {Editor of scientific manuscripts for non-native English speakers}
    {Freelance Editor for Scientific Papers}
    {Global}
    {2010 - 2014}
    {
      \begin{cvitems}
        \item {Edited scientific manuscripts for non-native English speakers leading to publication in high profile scientific journals, including work for American Journal Experts, a global editing service for scientists.}
        \item {Built Joomla site (pre-web dev days) to advertise my services. Brought in business by advertising on Austrian websites.}
      \end{cvitems}
    }
    
  \cventry
    {Simulation \& Modeling of Metallurgical Processes}
    {Post Doctoral Research – University of Leoben, Austria}
    {Leoben, Austria}
    {2006 - 2010}
    {
      \begin{cvitems}
        \item {Created a computational model of a large casting process to simulate flow and heat transfer phenomena for an Austrian steel making company.}
        \item {Expanded functionality of commercial simulation software with user defined functions in C and data processing scripts in scheme. Used Matlab extensively for data analysis. Tested feasibility of open source simulation framework, OpenFOAM.}
        \item {Defined experimental investigations for industry partner to get input and validation data for simulations.}
      \end{cvitems}
    }
    
\end{cventries}
