%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-emerald}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Autumn Fjeld}{}
% \address{San Francisco, CA}
\mobile{(+1) 415-810-4344} 
%%% Social
\email{autumnfjeld@gmail.com}
\homepage{autumnfjeld.com}
\github{autumnfjeld}
\linkedin{autumnfjeld}
%%% Optionals
% \position{Software Engineer{\enskip\cdotp\enskip}Security Expert}
\position{Software Engineer{\enskip\cdotp\enskip}Web Developer}
% \quote{Moving from San Francisco to Sydney in mid November 2017. \\ Seeking a creative and challenging front-end or full-stack web development role.}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Letter Data (Cover Letter)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\recipient
  {LoungeBuddy}
  {}
\letterdate{\today}
\lettertitle{Application for Senior Web Engineer}
% \letteropening{Dear Loungebuddies,}
\letterclosing{Sincerely,}
% \letterenclosure[Attached]{Curriculum Vitae}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Autumn Fjeld~~~·~~~Cover Letter}
  {}

\begin{document}

%%% Make a header for CV using personal data
\makecvheader

%%% Make a title for Cover Letter using letter data
\makelettertitle

%%% Write content for your cover letter
\begin{cvletter}
\raggedright
\vspace{-10pt}
\cvparagraph{About Me}
Hello! I am moving from San Francisco to Sydney in November 2017 and am starting my job search for a 
% front-end or full stack 
web development position at a company that fosters innovation, continual learning, and a collaborative work environment.  I lean towards the front-end side of web development and am happiest when turning code into visuals that create a happy, intuitive user experience. An ideal role for me would also include opportunities to work on all parts of a codebase.
\vspace{6pt}
\\
I have close to four years web development experience and decades of analytic problem solving experience from my academic career in materials science and fluid dynamics. 
My first development job was at a small chaotic start-up, one of four engineers building a hybrid mobile app and an enterprise website, with a fun, modern tech stack. I was quickly trusted to work independently, in all parts of codebase, and regularly implemented my own UI layouts.  After two happy years at this start-up, I decided I needed new challenges and a more structured team environment and I moved to a larger company and into a huge codebase with a complicated tech stack and a wonderfully structured agile/scrum team process.  I participate in design meetings with our Product Lead and design team, an excellent learning experience in how to design for the customer.  
\vspace{6pt}
% From these two jobs, spanning many years, I have experienced a range of working, coding, and learning styles among countless other wonderful things. \\
\\
I thrive on travel. I went to Cuba in May and loved the vibrant, colorful culture. Previous off-the-beaten path trips include NYE in the Republic of Georgia, a trip to Ghana and Togo to visit a friend in the Peace Core, and Nicaragua. I lived in Austria for over four years, learned German, and took every opportunity to explore Europe.  Now I'm fortunate enough to be relocating to a new part of the world and another adventure begins!
%  I am an American citizen and have an Australian work visa (sponsored by UNSW where my husband was recently hired as an Assistant Professor), which my visa grant notice describes as: Class UC, subclass 457.

% In my current role at a larger company I sit in on design meetings with our Product Lead and design team to absorb and contribute as much as possible.  

\vspace{-3pt}
\cvparagraph{Why LoungeBuddy?}
I have been eyeing LoungeBuddy for some time, as it would be fabulous to code for a company that is all about travel. I am now in a position to reach out and learn more about LoungBuddy, and perhaps make what sounds like a potential dream job into a reality with my migration south. Tech-wise, my ideal position would be a return to Node and Angular, the tech stack I worked in a couple years ago, and which fits LoungeBuddy's needs.  I find both Node and Angular fun and intuitive.  
\vspace{6pt}
\\
The fact that LoungeBuddy is based in my favorite city and my soon-to-be new home is a wonderful bonus. :)

\vspace{-3pt}
\cvparagraph{Why Me?}
I am a thorough, logical coder and a creative problem solver---happy to think out of the box when there is a need for new architecture or UI design.  As a software developer who cares deeply about creating a great, customer-centric UI, I believe my goals are closely aligned with LoungeBuddy's standards and efforts for constant improvement.  My favorite part of web development is building a product consumed by people (in contrast to my academic research career which for me lacked a human element). I have a good eye for layout and for building features that are intuitive for a user.
\vspace{6pt}
\\
% Anything I don’t know I can learn and hope I am always learning something new, a critical ingredient of a satisfying job.
I love to learn and my academic background has trained me to put forth the extra effort to get to the end goal. I finally found a career I love---building products that delight people, and I know that enthusiasm comes through in my work. You can look me up at \href{http://autumnfjeld.com}{autumnfjeld.com}.



\end{cvletter}

%%% Make a closing for Cover Letter using letter data
\makeletterclosing

\end{document}
