\documentclass[11pt]{res} % default is 10 pt
\usepackage{paratype}
 \renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif
% \usepackage[T1]{fontenc}
% \usepackage{lmodern}
%\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newsectionwidth{10pt}  % So the text is not indented under section headings
\usepackage{anysize}
\marginsize{.7in}{1in}{.8in}{.5in}    %{left}{right}{top}{bottom}
\renewcommand{\labelitemi}{\tiny{$\diamond$}}      
\usepackage[none]{hyphenat} 
\sloppy
\raggedright
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{tabularx}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\definecolor{AutGreen}{HTML} {006400}
\definecolor{DarkGray}{gray}{0.3}
% \usepackage{fancyhdr}
% \pagestyle{fancy}
% \headheight 61pt
% \headsep 10pt
% \renewcommand{\headrulewidth}{0pt}
% %\fancyheadoffset [R] {50pt}
% \rfoot{{\small \color{AutGreen}Autumn Fjeld \\autumnfjeld@gmail.com} \\ \smallskip \\{\color{AutGreen}\hrule }}

\usepackage{tikz}
\usetikzlibrary{arrows}
\newcommand{\myrule} [3] []{
    \begin{center}
        \begin{tikzpicture}
        \hspace{-6pt}
            \draw[#2-#3, thick, #1] (0,0) to (\linewidth,0);
        \end{tikzpicture}
    \end{center}
}
% formatting for title info
\newcommand\details[1]{\vspace{-21pt}\color{AutGreen}\begin{center}\small{#1}\end{center}\vspace{-14pt}}

 %\rhead{{\color{AutGreen} \small Autumn Fjeld \\ autumnfjeld@gmail.com} \\ \medskip \\{\color{AutGreen}\hrule }}
\pagenumbering{empty}


\begin{document} 
\thispagestyle{plain}
\vspace{-50pt}
 \name{ {\sc {\LARGE \color{AutGreen} {\sc Autumn Fjeld}}} \\[2pt]} % the \\[pt] adds a blank line after name

% \vspace{-20pt}
% \color{AutGreen} 
% \address{ 878 Capp Street \\   San Francisco, CA 94110  } 
% \address{ \hspace{34pt} 415-810-4344\\  autumn@nmutua.com }

\begin{resume}
\details{878 Capp Street - San Francisco, CA - 415-810-4344 - autumnfjeld@gmail.com }
\vspace{2pt}
\details{  github.com/autumnfjeld - linkedin.com/in/autumnfjeld - twitter.com/autaut }
\vspace{-32pt}
\color{AutGreen}{  \myrule{o}{o} }
\color{DarkGray}
\vspace{-10pt}  
\section{EDUCATION} 
\vspace{4pt}
 \textbf{  Software Engineering Immersive} JavaScript \& Modern Frameworks \hfill {\it Hack Reactor, San Francisco} \\
% \hspace*{20pt} Javascript \& Frameworks  April 2014 \\
 \textbf{ Ph.D. \& M.S.} Materials Science \& Engineering   \hfill {\it University of California, Berkeley} \\
 \textbf{ B.S.} Chemical Engineering, {\it Magna Cum Laude} \hfill {\it Arizona State University } 

%-------------------------------------------------------------------------------------------
% \vspace{-4pt}
\section{LANGUAGES \& TECHNOLOGIES}
\begin{itemize} \itemsep -1pt 
  \item Experienced: JavaScript, HTML/CSS, AngularJS, Jasmine, Firebase, d3.js, Matlab, Bootstrap, Stylus, SASS, Backbone, jQuery, Adobe Illustrator, Jasmine, Node, Mongo, Unix scripting, {\fontfamily{}\selectfont \LaTeX }
  \item Familiar:  PHP, Yii, Scheme, C, Express, Ionic, Cordova, Ruby, Sinatra, Protractor, Photoshop 
\end{itemize}
%
%-------------------------------------------------------------------------------------------
% \vspace{-8pt}
\section{ EXPERIENCE} 
\vspace{4pt}
\textbf{TalentBin by Monster}  \hspace{6pt}  \textit {Software Engineer}  \hfill San Francisco, CA April 2016--Present \\
\textit {Passive recruiting software}
\vspace{2pt}
\begin{itemize} \itemsep -1pt 
  \item Working to phase out legacy code (PHP, Yii, YUI) and architect new code patterns with modern frameworks (Ractive, Backbone, Single Page Apps).
  \item As a new team member, helping a growing team migrate from unstructured startup culture to a well-defined agile-scrum work process. Creating documentation, proactively recommend improvements in communication and tools (git, slack, zapier, etc.).
  \item Co-supervising two computer science interns.
\end{itemize}
%
\vspace{-6pt}
\textbf{Ziploop}  \hspace{6pt}  \textit {Senior Front End Developer}                \hfill Orinda, CA 2014--April 2016 \\
\textit {Mobile shopping organizer and retail portal for retailer to consumer rewards}
\vspace{2pt}
\begin{itemize} \itemsep -1pt 
  \item Designed and implemented front-end features for mobile consumer app and two enterprise sites in AngularJS framework.  Worked closely with President to design UI/UX.
  \item Collaborated with founding CTO to architect components, maintain build processes (grunt, gulp, git, unix scripts), choose frameworks, modules, and push to keep a clean, maintainable code base.
  \item Pro-actively presented app design changes and modernizations that were routinely accepted.  
  \item Refactored many parts of chaotic, legacy codebase to maintainability and sanity; solved load time problems for large list of images, optimizing quality and performance; continually strove for pixel perfect UI/UX.
  \item Managed collaborations between lead developer and non-technical president, supervised two junior engineers and an assistant to develop her technical graphic design skills.
\end{itemize}
%
\vspace{-6pt}
\textbf{Plentyy}                    \hfill San Francisco, CA 2014 \\
\textit {Mobile app that connects users to last-minute bargain deals with local merchants}
\vspace{2pt}
\begin{itemize} \itemsep -1pt 
  \item Designed back-end schema in Firebase, chosen for Simplelogin authentication, direct database reference binding, and fast prototyping for MVP.
  \item Built app in AngularJS architecture, ported to mobile with Cordova and styled with Ionic. Careful attention given to AngularJS controller and service modularity to create efficient team workflow.
\end{itemize}
%
\vspace{-6pt}
\textbf{WikiViz Project} \hfill San Francisco, CA 2014 \\
\textit{Visualization tool of relationships between Wikipedia articles}
\vspace{2pt}
\begin{itemize} \itemsep -1pt 
  \item Built a d3.js interactive force directed graph in an AngularJS directive, allowing users to click on a url-node to create an expansive node map of Wikipedia articles.
  \item Built AngularJS components to communicate with back-end API, parse data into d3.js algorithms. 
\end{itemize}
%
% \vspace{-10pt}
% \textbf{Political Poke}      \hfill San Francisco, CA 2014 \\
% \begin{itemize} \itemsep -1pt 
%   \item Hackathon project built in AngularJS, user enters a politician's name to retrieve political campaign contribution data pulled from New York Times API. 
% \end{itemize}

%-------------------------------------------------------------------------------------------
\vspace{-6pt}
\section{TECHNICAL EXPERIENCE} 
\vspace{4pt}
\textbf{Technical Support Engineer -- NUMECA International} \hfill  San Francisco, CA 2010--2013\\
\textit{ Engineering Support \& Business Development}
\vspace{2pt}
\begin{itemize} \itemsep -1pt 
	\item Provided consulting support to engineers at Boeing, Honeywell, etc. on using NUMECA's computational fluid dynamics software tools, delivering solutions in meshing, solver setup, and post-processing. 
	\item Improved software as an integral part of the feedback loop for identifying and troubleshooting software bugs, user-friendliness, and scientific accuracy issues.
	\item Developed and delivered technical training webinars twice a month to NUMECA's user base. 
\end{itemize}
% \clearpage
% \hspace{10pt}  %hack to force vspace to be recognized
\vspace{10pt}\\
\textbf{Freelance Science Editor}              \hfill Global 2010--2014\\
\textit {Editor of scientific manuscripts for non-native English speakers}
\vspace{2pt}
\begin{itemize} \itemsep -1pt 
  \item Edited scientific manuscripts for non-native English speakers leading to publication in high profile scientific journals, including work for American Journal Experts, a global editing service for scientists.
    \item Built Joomla site to advertise my services. Brought in business by advertising on Austrian websites. 
\end{itemize}
%
\vspace{-8pt}
\textbf{Post Doctoral Research -- University of Leoben, Austria} \\
\textit{Simulation \& Modeling of Metallurgical Processes} \hfill  Leoben, Austria 2006--2010
\vspace{2pt}
\begin{itemize} \itemsep -1pt  % reduce space between items
\item Created a computational model of a large casting process to simulate flow and heat transfer phenomena for an Austrian steel making company.
 \item Expanded functionality of commercial simulation software with user defined functions in C and data processing scripts in scheme.  Used Matlab extensively for data analysis. Tested feasibility of open source simulation framework, OpenFOAM.
\item Defined experimental investigations for industry partner to get input and validation data for  simulations.
\end{itemize}
%
\vspace{-8pt}
\textbf{Ph.D. -- University of California, Berkeley} \\
\textit{Materials Science \& Engineering}              \hfill  Berkeley, CA 2001--2006 
\vspace{2pt}
\begin{itemize} \itemsep -1pt 
	\item Collaborated in a five year project with Alcoa, Inc. to optimize a molten aluminum purification process, with specific goals to reduce toxic chloride emissions and improve energy efficiency.
	\item Ran fluid dynamics simulations of the purification process to assess mixing, residence time, bubble distribution to find optimum operating conditions, validating results with experimental data.
	\item Built a bubble probe to use in motel aluminum experiments to detect capacitance change on bubble contact.
%\item Utilized a variety of computational and data analysis tools: Femlab, FLUENT, Matlab, Mathematica, GAMBIT
    \item Received student nominated outstanding teaching award as graduate student instructor for undergraduate materials science lab.
\end{itemize}
% \vspace{-10pt}
%
% \textbf{ M.S. -- University of California, Berkeley} \\
% \textit{ Materials Science \& Engineering}           \hfill Berkeley, CA 1999--2001
% \begin{itemize} \itemsep -1pt 
% 	\item Researched and developed experimental thin films for supported liquid membranes for aqueous filtering of acetic acid.
% 	\item Investigated processing techniques and properties of epoxy films applied to a membrane
% surface to seal liquid extractant into pores of supporting membrane.
% \end{itemize}
%
%--------------------------------------------------------------------------------
 \vspace{4pt}
\section{FUN FACTS ABOUT ME} 
 \vspace{15pt}
\begin{itemize}  \itemsep -1pt 
	\item Traveling and checking out the world is a must! Recent trips include the Republic of Georgia, Spain, Portugal, and Colombia. 
	\item Love to read, explore San Francisco and the Bay, ride my bike, eat well and drink well. 
  \item Started weekly German-learning conversational group for foreigners in Leoben, Austria. Keep up with my German via social groups and classes at local community college.
  \item Occasional sewer and creator of colorful clothes, jewelery, bags.
	\item Past volunteer experiences: tutor for Women Who Code, high school prep classes for underprivileged kids.
\end{itemize} 
%---------------------------------------------------------------------------------  

%-------------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------------- 
%\section{REFERENCES}
% \vspace{15pt}   
%\begin{itemize} \itemsep 2pt  
%		\item[] Prof. Andreas Ludwig, Simulation and Modeling of Metallurgical Processes, Montanuniversit\"at Leoben, Leoben, Austria,  andreas.ludwig@mu-leoben.at, \hspace{15pt} +43 3842-402-3100  
%	\item[] Prof. James W. Evans, Materials Science and Mineral Engineering, U.C. Berkeley, Berkeley, CA 91720, vans@berkeley.edu, 510-642-3807 
%	\item[] Dr. Corleen Chesonis, Alcoa Inc., Alcoa Technical Center, Alcoa Center, PA 15069,  \hspace{15pt} corleen.chesonis@alcoa.com, 724-337-4794  
%	\item[] Dr. Jaime Kruzic, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University,	Corvallis, OR 97331, kruzicj@engr.orst.edu, 541-737-7027
%	\item[] Dr. Scott Beckman, Materials Science and Engineering, Iowa State University, Ames, IA 50011, sbeckman@iastate.edu, 515-294-1107                         
%\end{itemize}
%
\end{resume}
\end{document}
