\cvsection{Work Experience}
\begin{cventries}
  \cventry
    {Passive recruiting software}
    {Software Engineer - TalentBin by Monster}    
    {San Francisco, CA}
    {April 2016 - present}
    {
      \begin{cvitems}
        \item {Full-stack software engineer, with front-end emphasis. Build and maintain enterprise recruiting web application. Tech stack: MySQL, Java, PHP, Javascript (Backbone, Ractive).}
        \item {Work to enforce good design within our team, provide constructive criticism on our UI. Am engaged with product manager and design team in a major redesign of our site--learning about a large scale redesign process while offering a front-end engineer's perspective.}
        \item {Propose new code patterns with modern frameworks to replace, or coexist with legacy code.}
        \item {Building a chrome extension app: a mini-version of our main site that pulls data from social network sites to match profiles in our db.}
        \item {Periodically work on back end projects in JAVA, Python, AWS configuration, and MySQL database scripts.}
        \item {Part of a growing team migrating from start-up culture to a well-defined agile-scrum process. I create documentation, proactively recommend improvements in communication and tools (git, slack, zapier, etc.).}
        \item {Have supervised two computer science interns each summer, guiding them through the complexities of a large codebase and teaching about front-end web development.}
      \end{cvitems}
    }
  \cventry
    {Mobile shopping organizer and retail portal for retailer to consumer rewards}
    {Senior Front End Developer{\enskip\cdotp\enskip}Ziploop }
    {Orinda, CA}
    {April 2014 - April 2016}
    {
      \begin{cvitems}
        \item {Designed and implemented front-end components of mobile consumer app and two enterprise sites in AngularJS framework. Worked closely with President to design UI/UX.}
        \item {Collaborated with founding CTO to architect components, maintain build processes (grunt, gulp, git, unix scripts), choose frameworks, modules, and pushed to keep a clean, maintainable code base.}
        \item {Refactored many parts of chaotic, legacy codebase to maintainability and sanity (SASS, Angular best practices)
        \item Solved load time problems for large list of images, optimizing quality and performance; continually strove for pixel perfect UI/UX.}
        \item {Managed collaborations between lead developer and non-technical president, supervised two junior engineers and an assistant to develop her technical graphic design skills.}
      \end{cvitems}
    }
  \cventry
    {Project based software immersive course}
    {Student{\enskip\cdotp\enskip} Hack Reactor}
    {San Francisco}
    {January 2014 - April 2014}
    {
      \begin{cvitems}
        \item {Part of a team contracted to develop a prototype for a commercial app. Designed back-end schema in Firebase, chosen for Simplelogin authentication, direct database reference binding.}
        \item {Built app in AngularJS architecture, ported to mobile with Cordova and styled with Ionic. Careful attention given to AngularJS controller and service modularity to create efficient team work-flow.}
        \item {Built \href{http://wikiviz.herokuapp.com}{wikiviz}, a d3.js interactive force directed graph as an AngularJS directive, allowing users to click on a url-node to create an expansive node map of Wikipedia articles.}
      \end{cvitems} 
    }
  \cventry
    {Engineering Support/Consulting \& Business Development}
    {Technical Support Engineer – NUMECA International}
    {San Francisco, CA}
    {November 2010 - July 2013}
    {
      \begin{cvitems}
        \item {Provided consulting support to engineers at Boeing, Honeywell, etc. on using NUMECA’s computational fluid dynamics software tools, delivering solutions in meshing, solver setup, and post-processing.}
        \item {Improved fluid dynamics and meshing software as an integral part of the feedback loop for identifying and troubleshooting software bugs, user-friendliness, and scientific accuracy issues.}
        \item Created and delivered technical training webinars twice a month to NUMECA’s user base.
      \end{cvitems}
    }
  \cventry
    {Editor of scientific manuscripts for non-native English speakers}
    {Freelance Editor for Scientific Papers}
    {Global}
    {2010 - 2014}
    {
      \begin{cvitems}
        \item {Edited scientific manuscripts for non-native English speakers leading to publication in high profile scientific journals, including work for American Journal Experts, a global editing service for scientists.}
        \item {Built Joomla site (pre-web dev days) to advertise my services. Brought in business by advertising on Austrian websites.}
      \end{cvitems}
    }
  \cventry
    {Simulation \& Modeling of Metallurgical Processes}
    {Post Doctoral Research – University of Leoben, Austria}
    {Leoben, Austria}
    {2006 - 2010}
    {
      \begin{cvitems}
        \item {Created a computational model of a large casting process to simulate flow and heat transfer phenomena for an Austrian steel making company. Defined experimental investigations for industry partner to get input and validation data for simulations.}
        \item {Expanded functionality of commercial simulation software with user defined functions in C and data processing scripts in scheme. Used Matlab extensively for data analysis. Tested feasibility of open source simulation framework, OpenFOAM.}
      \end{cvitems}
    }
\end{cventries}
