\cvsection{PersonalProjects}
\begin{cventries}
  \cventry
    {Website for research group at University of California, Riverside}
    {Freelance Website Project}
    {My house}
    {May 2017 - present}
    {
      \begin{cvitems}
        \item {Building a static-ish site for a Computational Materials research group at the University of California Riverside utilizing AWS tools: hosted on S3, using API Microservices and lambda functions to handle dynamic content. \href{https://github.com/autumnfjeld/dralexgreaney}{github.com/autumnfjeld/dralexgreaney}} 
        \item {Technical goals for this freelance project include maximizing use of flexbox, using npm for all build steps, creating custom node scripts to compile pug templates and parse \href{http://www.bibtex.org/About}{bibtex} journal citations into JSON format.}
      \end{cvitems}
    }
  \cventry
    {Coursera's Graphic Design Specialization}
    {Online Design Course}
    {Coursera.org}
    {March 2017 - present}
    {
      \begin{cvitems}
        \item {Improving my design skills. Currently enrolled in \href{https://www.coursera.org/specializations/graphic-design}{Coursera's Graphic Design Specialization} created by California Institute of the Arts. Courses included Typography, Composition, Creative Iteration, and more.} 
        \item {Capstone project will be to produce personal brand in poster, business cards, and website. Course progress is ongoing.}
      \end{cvitems}
    }
  \cventry
    {autumnfjeld.com}
    {My Website Resume}
    {My house}
    {2016 - present}
    {
      \begin{cvitems}
        \item { Built \href{http://autumnfjeld.com}{autumnfjeld.com} from a pre-designed the HTML/CSS template and made it my own, which has been a great learning experience in design and layout. Broke up the HTML into pug files, storing my content as JSON to compile into a static site stored on AWS S3.}    
        \item {Connected my email to this domain via Simple Email Service and wired up a Lambda function to email the form content from my API endpoint to myself.} 
      \end{cvitems}
    }    
\end{cventries}
